---
title: "Market Basket Analysis of Buying Baseball Equipment"
author: "Ryan Eberle"
date: "December 7, 2018"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


**For this post I will use market basket techniques with the arules package in R to study customer buying behavior of baseball equipment at local sports store.**

```{r}
library(arules)
library(arulesViz)

data <- read.csv("Baseball_Gear.csv", row.names=1)
data<-as.matrix(data)
rules<-apriori(data)
inspect(rules)

```


**Looking at the top association rules based on highest lift.**

```{r}
rules.sorted <- sort(rules, by="lift")
lift_top3<-rules.sorted[0:3]
inspect(lift_top3)
```

*What the lift means for our first rule is that customers are 3.69 times more likely to buy baseballs if they buy a glove.  Likewise, the second rule is that customers are 2.73 times more likely to buy cleats if they buy batting gloves, socks, and pants at the store.*


**Looking at the top association rules based on highest confidence.**

```{r}
rules.sorted <- sort(rules, by="confidence")
conf_top3<-rules.sorted[0:3]
inspect(conf_top3)
```

*What the confidence means for our first rule is that 95.9% of the time that batting gloves, socks, and pants were bought, cleats were bought as well.  Likewise, the second rule is that 93% of the time that batting gloves and cleats were bought, socks were bought as well.  Finally, the last rule is that 92.7% of the time that helmets and belts were bought, pants were bought too.*


**Looking at the top association rules based on highest support.**

```{r}
rules.sorted <- sort(rules, by="support")
conf_top3<-rules.sorted[0:3]
inspect(conf_top3)
```

*What support means for our rules is how frequently these items were bought in the total dataset.  So 31.9% of the purchases included socks and cleats.* 


**Different types of plots showing the rules based on their confidence, support, and lift.**

```{r}
plot(rules)
plot(rules, method = "grouped")
plot(rules, method = "graph")
plot(rules, method = "paracoord", control = list(reorder = TRUE))
```

