---
title: "Kmeans Clustering"
author: "Ryan Eberle"
date: "December 10, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**For this post I will examine a data set of home improvement customers to help give insight into what the customer base looks like.**

**First lets do a little data exploration to see what our customer base looks like.**
```{r}
#read data
cust<-read.csv("Home_Customers.csv")

head(cust)
str(cust)

#How many customers rent their home (1) vs own their home (0)
table(cust$rent)
#How many customers have a garden at their home (1 means yes 0 means no)
table(cust$garden)
#How many customers are male(1) vs female(0)
table(cust$gender)
#The age of the customers
hist(cust$age)
table(cust$age)
#It appears there are some incorrect values as it does not make sense for a customer of a home improvement store to be under 10 years of age.
```

*Based on our data exploration, we can tell that the majority of our customer base is male, owns their house, has a garden at thier house, and is between 30-60 years old.*


**Now we are going to do some K-means clustering of our data base to break our customers into segments to target specific groups for marketing purposes.**
```{r}
set.seed(1)
fit<-kmeans(cust, 5)

#Trying to find the optimal number of clusters
SSEs <- rep(NA,10) 
SSEs[1] <- fit$totss 
for(k in 2:10){
	fit <- kmeans(cust, k)
	SSEs[k] <- fit$withinss
}
par(mar=c(4,4,1,1))

plot(1:10,SSEs,type="b",xlab="Number of Clusters")

#The optimal number of clusters is 4
fit<-kmeans(cust, 4)
fit$center

```
*Our clusters tell us 2 things.  First, that the main difference in the clusters is the average age of each cluster.  Second, the younger clusters are more likely to rent their house, not have a garden, and be female.  Based on all these results, we should do most of our marketing to middle-aged males that own their house and have a garden.  Furthermore, their may be room to expand our customer base to the younger generation if we target females that may or may not own their own home yet.*
